---
title: "PSTAT 10 Worksheet 2"
subtitle: "Due 6/26/2024 11:59pm"
author: "Sou Hamura"
output: pdf_document
---

# Problem 1: Basic vector manipulation

1. Recall from lecture my 2023 monthly gas bill in order was given by:

```{r}
gasbill <- c(46, 33, 39, 37, 46, 30, 48, 32, 49, 35, 30, 48)
```

It turns out the charge for December should have been 49 instead of 48. Update 
the ```gasbill``` to reflect the true charge. Try not to “cheat” and just type 
in all the old values again; use the existing ```gasbill``` vector.

```{r}
gasbill[12] <- 49
gasbill
```


2. Recreate the following numeric vector. Avoid typing in all of the values manually.

```{r, eval=FALSE}

dec <- seq(-50, -54)
inc <- seq(-53, -50)
seq1.2 <- c(dec, inc)
seq1.2

## [1] -50 -51 -52 -53 -54 -53 -52 -51 -50
```

3. Create a vector from 1 to 10 with increments of 0.05. What is the length of this vector? Hint: Use `seq` with `by` argument.

`#Function

```{r}
vec1.3 <- seq(1, 10, by=0.05)
length(vec1.3)
```

4. Create a vector of length 100 from 1 to 10 with uniform increments. What is the increment? Hint: Use `seq` with `length` argument.

```{r}
vec1.4 <- seq(1, 10, length.out = 100)
vec1.4[2] - vec1.4[1]
```

5. What happens if you try to use `seq` with both the `length` and `by` arguments specified?

#when we try to use "seq" function with both the "length" and "by" arguments specified, an error will occer because there are too many arguments

# Problem 2

Download the file `ws2.csv` from the course website and import it into R. This data set has two variables named `x` and `y`.

Make sure to change your `here()` function to point to your `ws2.csv` file.

```{r}
ws2_df <- read.csv("ws2.csv")
summary(ws2_df)
```

Remember the variables in a data frame are accessed by name with the dollar sign (and that the result is a vector).

1. Determine the lengths of x and y.

```{r}
length(ws2_df$x)
length(ws2_df$y)
```

2. What is the 40th element of x and the 80th element of y?
```{r}
ws2_df$x[40]
ws2_df$y[80]
```


3. What is the average of all the values in the data frame, including both x and y?
```{r}

x_sum <- sum(ws2_df$x)
y_sum <- sum(ws2_df$y)
x_len <- length(ws2_df$x)
y_len <- length(ws2_df$y)
x_avg <- x_sum / x_len
y_avg <- y_sum / y_len
average <- (x_avg + y_avg) / 2
average
```

4. How many elements of x are greater than 70?
```{r}
X_70 <- ws2_df$x[ws2_df$x > 70]
length(X_70)

```


Let’s look at the first 4 elements of x and y:

```{r}
ws2_df$x[1:4]
## [1] 74 89 78 23
ws2_df$y[1:4]
## [1] 58 26 48 80
```

The first three elements of x are greater than or equal to their corresponding 
element in y: $74 > 58$, $89 > 26$, $78 > 48$. But the fourth element of `x`, 
23, is less than the fourth element of `y`, 80.

5. How many elements of x are greater than or equal to the corresponding element in y?
```{r}
x_greater_y <- ws2_df$x[ws2_df$x >= ws2_df$y]
length(x_greater_y)

```
6. What is the proportion of elements of x that are greater than or equal to the corresponding element in
y?
```{r}
x_greater_y <- ws2_df$x[ws2_df$x >= ws2_df$y]
num_xy <- length(x_greater_y)
total <- length(ws2_df$x)
num_xy / total

```
7. How many values in x differ from their corresponding value in y by more than 10 in absolute value?
Hint: there is an `abs` function.

```{r}
x_val <- ws2_df$x
y_val <- ws2_df$y
diff_xy <- y_val - x_val 
abs_diff <- abs(diff_xy)
diff_10 <- abs_diff[abs_diff > 10]
length(diff_10)

```

# Problem 3

Create a vector of integers from 1 to 12 inclusive.
```{r}
vec_p3 <- 1:12
```

1. Use the vector to create a 3x4 matrix. Did recycling occur?

```{r}
matrix(vec_p3, nrow=3, ncol=4)

```
# recycling did not occur

2. Use the vector to create a 4x4 matrix. Did recycling occur?
```{r}
matrix(vec_p3, nrow=4, ncol=4)

```
# recycling did occur

# Problem 4

Use the heights_df data frame from worksheet 1. The height variable is given in centimeters (cm).

1. Write a vectorized function cm_to_inch that takes a numeric centimeter and converts it to inches.

Apply the function to the height vector. First 10 elements are shown below:

```{r}
heights_df <- read.csv("heights.csv")
summary(heights_df)
```

```{r}

cm_to_inch <- function(cm){cm * 0.39}

head(cm_to_inch(heights_df$height), 10) # the head function gives the first elements
## [1] 62.40 67.08 65.52 71.37 68.25 73.71 60.84 65.13 76.05 64.35
```

2. Write a vectorized function cm_to_ft_inch that converts numerical values given in cm to a feet inch format, rounding to the nearest inch.
For example,

```{r}
heights_df <- read.csv("heights.csv")
summary(heights_df)
```

```{r}

cm_to_ft_inch <- function(cm){
  inches <- cm_to_inch(cm)
  r_inches <- round(inches)
  ft <- (r_inches %/% 12)
  inch <- (r_inches %% 12)
  s_ft <- as.character(ft)
  s_inch <- as.character(inch)
  return(paste(s_ft, s_inch))}

cm_to_ft_inch(178)
## [1] "5 9"
```

You may need the (vectorized) quotient function %/% and the remainder function %%:

```{r}
# Quotient: 3 goes into 7 two times
7 %/% 3
## [1] 2
# Remainder: The remainder when 7 is divided by 3 is one
7 %% 3
## [1] 1
```

Remember you should look things up on StackOverflow if you’re stuck with some operations.
Apply the function to the height vector.

```{r}
head(cm_to_ft_inch(heights_df$height), 10)
## [1] "5 2" "5 7" "5 6" "5 11" "5 8" "6 2" "5 1" "5 5" "6 4" "5 4"
```