---
title: "PSTAT 10 Worksheet 7"
author: "Sou Hamura"
date: "2024-07-18"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}

library(RSQLite)
library(sqldf)
library(DBI)
chinook_db <- dbConnect(SQLite(), "Chinook_Sqlite.sqlite")
dbExecute(chinook_db, "pragma foreign_keys = on")


```

## Problem 1: Terminology

#Primary keys must be unique (and not NULL)
#Foreign keys must reference existing primary keys or be NULLr we are working with a relational database, following a relational data model.


1. Briefly explain the purpose of primary keys and foreign keys in a relational database.

# The difference between two keys create constraints which enforce the integrity of a database

2. Briefly explain how relational databases model real world data.

# Relational databases organize information into tables to make it easier understand how different data structures relate to each other.

3. Briefly explain the difference between SQL, SQLite, and RSQLite.

# SQL is a language designed to create, read data from, and write data to relational databases. SQLite is designed for simple applications and it's provided by the RSQLite package in R.

## Problem 2: Foreign keys

```{r}

db_table <- dbListTables(chinook_db)
for (i in seq_along(db_table)){
  print(dbGetQuery(chinook_db, paste0("pragma foreign_key_list(", db_table[i], ")")))
}

```

1. Album.ArtistId -> Artist.ArtistId
2. Customer.SupportRepId -> Employee.EmployeeId
3. Employee.ReportsTo -> Employee.EmployeeId
4. Invoice.CustomerId -> Customer.CustomerId
5. InvoiceLine.TrackId -> Track.TrackId
6. InvoiceLine.InvoiceId -> Invoice.InvoiceId
7. PlaylistTrack.TrackId -> Track.TrackId
8. PlaylistTrack.PlaylistId -> Playlist.PlaylistId
9. Track.MediaTypeId -> MediaType.MediaTypeId
10. Track.GenreId -> Genre.GenreId
11. Track.AlbumId -> Album.AlbumId


## Problem 3: Customer

1. Select the CustomerId, FirstName, LastName, State, Country of all customers living in California.

```{r}

dbGetQuery(chinook_db, "select CustomerId, FirstName, LastName, State, country from customer where State = 'CA'")

```

2. How many customers are from Brazil?

```{r}

dbGetQuery(chinook_db, "select count(*) from customer where Country = 'Brazil'")

```


