---
title: "PSTAT 10 Worksheet 8"
author: "Sou Hamura"
date: "2024-07-22"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(RSQLite)
library(sqldf)
library(DBI)
chinook_db <- dbConnect(SQLite(), "Chinook_Sqlite.sqlite")

```

## Problem 1

1. What is the total length in minutes of all tracks with GenreId = 2?

```{r}

dbGetQuery(chinook_db, "select GenreId, sum(Milliseconds)/60000 as minutes from Track
           where Track.GenreId = 2")

```

2. Using a join, add the name of the genre to the above query.

```{r}

dbGetQuery(chinook_db, "select Genre.Name, Track.GenreId,  sum(Milliseconds)/60000 as minutes from Track
           inner join Genre on Track.GenreId = Genre.GenreId
           where Track.GenreId = 2")

```
3. Using a group by, find this information for all genres. I’ve provided just the first 5 records of the output.

```{r}

dbGetQuery(chinook_db, "select Genre.Name, Track.GenreId,  sum(Milliseconds)/60000 as minutes from Track
           inner join Genre on Track.GenreId = Genre.GenreId
           group by Track.GenreId, Genre.Name")

```

## Problem 2


```{r}

dbGetQuery(chinook_db, "select EmployeeId as RepId, e.FirstName as RepFirstName, e.LastName as RepLastName, CustomerId, c.FirstName as CustFirstName, c.LastName as CustLastName from Customer c INNER JOIN Employee e ON c.SupportRepID = e.EmployeeId
           WHERE c.FirstName = 'Heather' AND c.LastName = 'Leacock'")

```


## Problem 3

1. How many difference countries are the customers from?
```{r}

dbGetQuery(chinook_db, "select distinct count(Country) from Customer")

```


2. Retrieve the unique titles of the employees.
```{r}

dbGetQuery(chinook_db, "select distinct title from Employee")

```
3. The following determines how many unique genres there are. Was distinct necessary here? Explain.

# No because the number of GenreId in Genre is already distributed according to the number of Genres



